Predicting the Quality of CDR-H3 Antibody Loop Structural Models

### 2022-12-19 paper.tex
Various text and layout cleanup

\documentclass[12pt]{article}
\bibliographystyle{unsrt}
\usepackage{a4}
\usepackage{graphicx}
\usepackage{url}
\usepackage{color}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}

@@

\begin{abstract}
  Therapeutic antibodies have shown an unprecedented pace of
  development and have brought new hope for the treatment of numerous
  diseases. Bioinformatics tools for modelling antibody structures
  have become invaluable for antibody engineering and the development
  of therapeutic antibodies. The antigen-binding site consists of six
  hypervariable loops, also known as the Complementary Determining
  Regions (CDRs), all of which can be modelled with high accuracy,
  except for CDR-H3, which generally has
  far greater length and sequence variability, with such great structural
  diversity, that modelling it is considerably harder.

  Many approaches for antibody modelling, such as our
  abYmod software, have been developed. Although such efforts have
  improved prediction accuracy, the results for CDR-H3 are
  still inconsistent and require further improvement. Providing a
  confidence score for the structure predictions would aid in
  differentiating well-modelled structures from incorrectly modelled
  structures, giving the abYmod user a clearer understanding of the
  generated 3D-model reliability.

@@

The variable
fragment (Fv) of an antibody contains the six complementarity determining regions
(CDRs, also known as hypervariable loops) which form the antigen binding site.
All except one of these loops can be clustered
into a limited number of `canonical structures'\cite{Al-Lazikani}. Therefore, modelling
these loops with adequate accuracy is commonly
achievable\cite{North2011}.  However, the CDR loop 3 of the 
heavy chain (CDR-H3) has a far greater sequence and length variability due to the
processes of V(D)J recombination and somatic hyper‐mutation and its
structure has remained unclassifiable\cite{Finn2016}. The variety in
structure is so great, that its structural diversity is remarkable
even compared to other protein loops\cite{Regep2017}. It was found
that over 75\% of CDR-H3 loops do not have a sub-{\AA}ngstr\"{o}m non-antibody
structural neighbour, while 30\% of CDR-H3 loops have a
completely unique structure compared with under 3\% for all non-antibody
loops\cite{Regep2017}.

@@

According to the Kabat definition, the CDR-H3 loop is made up of the
residues 95--105 (using the Kabat\cite{Kabat1992}, Chothia\cite{Al-Lazikani} or Martin\cite{Abhinandan2008} numbering schemes) in the heavy
chain, with a potential insertion site at position 100. The
possibility of such an insertion of a varying number of residues leads
to a large range of loop lengths, with bovine antibodies being
exceptionally long (Figure~\ref{fig:loopdist}).

For shorter loops, a higher prediction accuracy can be achieved than
for longer CDR-H3 loops. This was also shown by the Antibody Modelling
Assessments (AMA), two blind contests that required researchers to
build three-dimensional structural models (3D-models) from antibody sequences. The CDR-H3 loop
modelling quality achieved at the contests was on average much lower
for loops of longer lengths\cite{Almagro2011,Almagro2014}.

Several different approaches for generating 
3D-models from antibody sequences exist such as
RosettaAntibody\cite{Sircar2009,Sivasubramanian2009}, 
ABodyBuilder\cite{Leem2016}, PIGSPro\cite{Lepore2017}, Lyra\cite{Klausen2015}, AbLooper\cite{Abanades2022} and our own abYmod.
One of the most
used methods is RosettaAntibody, which implements template selection
and \emph{ab initio} CDR-H3 loop modelling using loop fragments and employing
specific angle restraints which bias the conformational space towards
so-called `kinked' loops\cite{Schoeder2021,Weitzner2017}. In
contrast, ABodyBuilder uses a database search algorithm
(FREAD\cite{Choi2010}) for CDR loop modelling.
abYmod \url{http://abymod.abysis.org/} utilizes extensive canonical
class definitions, \VHVL\ angle prediction and a large database of loop
structures (LoopDB) for CDR-H3 modelling.
Upon inputting an antibody sequence, abYmod assigns the
canonical class using a set of key residues\cite{Martin1996} and where
an exact match is not possible, a nearest class is identified.

abYmod selects light and heavy chains separately from PDB templates.
First these are selected on the basis of the number of matched
canonical classes and then on the basis of sequence identity.  The
\VHVL\ packing angle is currently selected from the parent that has
the best sequence identity over both chains, but an improved method is
currently in development. Any CDRs where there was no canonical match are then
are grafted onto the framework. If there is no template of the correct
length for CDR-H3, the loop is built using LoopDB, a database of
CDR-H3-like loops from all proteins. Finally, Gromacs energy
minimization software is used to optimize the 3D-model. This method has
proven very effective and preliminary analysis suggests the method
achieves comparable results, or outperforms, other modelling software
(see Results).

Using these mentioned modelling methods, framework regions can
generally be predicted with great accuracy (with better than 1\AA\
RMSD\cite{Almagro2014}), as one can often find a very similar
structure for the homology modelling process.  However, the CDR loops
are not as easily predicted due to their great diversity. If the
canonical conformation of CDR loops CDR-L1,L2,L3,H1,H2 can be identified, they too
can be modelled rather well, often within 1\AA\ \ca~RMSD, for CDR-H3 loops
the The average values are taken from the antibody modelling assessment average is usually above 3\AA\cite{Almagro2011}.

ABodyBuilder is a modelling server that provides the user with a
confidence score for each region (e.g.\ CDR-H2) of the antibody
3D-model. The given score is the probability that a specific region
(e.g.\ CDR-H2) will be will be modelled within a specific RMSD
threshold\cite{Leem2016}. Thus, it can be used to obtain an expected
RMSD value for a given probability (default 75\%). For the CDR-H3 this
score is calculated as a function of the loop length.  The confidence
scorer is described as robust, but less accurate in the case of CDR
loops due to the lack of data\cite{Leem2016}. ABLooper also provides a
confidence metric for the CDR-H3 loop 3D-model, which is estimated by the
diversity of a set of predicted conformations for the same
loop\cite{Abanades2022}. However, it remains unclear whether a high
prediction diversity score points towards loops with multiple
conformations or a low quality 3D-model. Furthermore, it remains unclear
how well the generated diversity score reflects 3D-model
quality\cite{Abanades2022}.

Modelling the CDR-H3 loop is a hurdle for \emph{in silico} development of
therapeutic antibodies. Currently, there is no definite, reliable way
to determine how accurate a generated structural 3D-model is within the
H3 region. Therefore, we have produced a
user-friendly predictor of CDR-H3 3D-model quality. The predictor will give
the user an RMSD-range in {\AA}ngstr\"{o}ms, in which the generated 3D-model lies
with a high probability.
This information can guide the
user in the antibody engineering process. The user has the choice to
determine whether the 3D-model is to be used as is, or
whether the 3D-model should be re-worked.

@@

The predictive power of any machine learning model (ML-model) is largely
dependent on the quality and size of the dataset on which it was trained. As
this is a non-linear, complex, multi-class classification problem, a
substantial amount of data was required. Thus, an extensive, verified
dataset of antibody structures called abYbank/AbDb\cite{Ferdous2018},
was utilised (1924 non-redundant
structures). The \ca\ root-mean-square deviation (RMSD) value
between the crystal structures
and modelled structures was calculated (see Methods) and
was used to classify 3D-models.

@@

After creating the feature dataset, it is pre-processed (cleaning,
scaling, encoding, see methods for details). Structures with a
resolution worse than 4\AA\ were removed.
Instances of antibodies in our non-redundant dataset that matched in loop sequence were
not removed. 3D-Models of some of these structures with the same loop
sequence differ significantly. The few large RMSD ranges may stem from
low resolution. For example, the loop sequence with the largest RMSD range 
has multiple structure files linked to it of varying quality, one of which has a resolution of only 3.00\AA. Residue differences near the loop may also
explain the conformational difference of the loop itself, 
even if the loop sequence does not differ. Some of these structures are
complexed while others are not, which may also affect the loop
structure (manuscript in preparation).

The target data (i.e.\ RMSD values) are transformed from numerical
values to nominal values so that they can be used for
classification. In order to define these nominal categories, the total
RMSD range must be divided into categories. This is done either by
creating uniform classes i.e.\ 1--2\AA, 2--3\AA, etc., (the optimal size of which
must be determined), or by creating balanced classes. When
creating balanced classes, the upper and lower thresholds of a
category are chosen in such a way that each class contains an equal
number of instances. This approach was chosen to counteract the
skewness of the RMSD distribution. However, this was found to
affect the final ML-model's predictive power negatively. Therefore,
uniform classes were used.

The RMSD values are also transformed into a set of binary values according to a
list of RMSD thresholds (i.e. a 1 is assigned to above and 0 to below a given threshold). This is done so that binary ML-models can be
trained, which will predict the probability e.g.\ that the 3D-model's RMSD
is above 2\AA, 2.2\AA, 2.4\AA, and so on. The number of binary
classifiers incorporated into the first layer has a great effect on
the final ML-model, the general trend being that the more binary
classifiers are used, the better the nominal prediction.

@@

As some features are in the form of amino acid names, these must be
encoded before they can be passed to a ML-model. The
encoding strategy often determines how efficiently the ML-model learns
and how much information can be extracted. Different strategies were
employed to represent protein sequences numerically, such as BLOSUM62\cite{Henikoff1992} and NLF\cite{Nanni2011} encoding (a non-linear Fisher transform of a large set of physicochemical properties). The four-feature physiochemical encoding strategy\cite{Abhinandan2010} was implemented for all ML-models, being
the most effective. However, PCA-3 BLOSUM62, a dimensionality-reduced
BLOSUM62 encoding method achieved comparable results.
Feature selection was conducted to improve the ML-model's learning
capacity. A high-dimensional feature dataset bears the risk of
introducing excessive noise, facilitating ML-model over-fitting and can be
responsible for an overall decrease in ML-model performance and
stability. Each additional input feature forces the ML-model to
handle a more complex task, which consumes excess computational power
and time and provides more variables leading to over-fitting of the ML-model.

Our ML-model was trained on different feature sets selected using manual
selection as well as algorithmic selection strategies (see methods), in order to
determine the most effective feature selection method. None of the
feature selection methods was a best fit for all ML-models. To create a ML-model implementing the encoding and feature selection strategies best suited for the specific ML-structure, a number of different combinations were tested, summarized in \ref{fig:results_table}. Additional ML-Models were discarded due to poor performance.

\begin{table}[]
\fontsize{12}{16}\selectfont
  \centering
  \caption{Summary of Machine-Learning Classifier Performances}
  \label{my-label}

  \begin{adjustbox}{width=\textwidth}

    \begin{tabularx}{\linewidth}{
    |>{\hsize=.35\hsize}X|% 10% of 4\hsize 
    >{\hsize=.4\hsize}X|% 30% of 4\hsize
    >{\hsize=.4\hsize}X|% 30% of 4\hsize 
    >{\hsize=.4\hsize}X|% 30% of 4\hsize
    >{\hsize=.4\hsize}X|% 30% of 4\hsize 
    >{\hsize=.4\hsize}X|% 30% of 4\hsize
    >{\hsize=.2\hsize}X|% 30% of 4\hsize
       % sum=4.0\hsize for 4 columns
  }
\hline
Features & Feature Selection Method & Optimi-zation Method& Multi/ Single-layer & First-layer weighted &Classifier Type & MCC\\
\hline
Basic & None & None & single & No & SVC & 0.54\\
Basic & None & Genetic Algorithm & single & No & SVC & 0.54 \\
All & None & None & single& No & Random Forest & 0.58\\
Selected & random forest feature selection & Genetic Algorithm & Single& No & Soft Voting & 0.59 \\
Selected & random forest feature selection & Genetic Algorithm & Multi& Yes & XGB & 0.63 \\
Selected & recursive feature elimination & Genetic Algorithm & Multi& Yes & XGB & 0.79 \\
Selected & recursive feature elimination & Genetic Algorithm & Multi& Yes & Decision-Tree & 0.99 \\
Selected (no log-file features) & recursive feature elimination & Genetic Algorithm & Multi& Yes & Voting(soft) & 0.92 \\
\hline
    \end{tabularx}

  \end{adjustbox}
\end{table}

@@

The best ML-model, and its best hyperparameters, are then determined for
each binary RMSD target. The set of binary ML-models outputs a number of
predictions that give the likelihood of the 3D-model having an RMSD above
the threshold value of the respective ML-model. These predictions are
then added to the feature set, on which a top-layer classifier is then
trained (Figure~\ref{fig:method}). Thus, a quasi-voting-system is incorporated into the final
classifier, in which a set of weaker classifiers vote on the ML-model
quality.

@@

\subsection{Machine Learning Model Performance}
The overall best final ML-model was composed of several different binary
classifiers, \ref{fig:flow} with an extreme gradient boosting (XGBoost) top-layer
nominal classifier. Features were selected using a recursive feature elimination algorithm, through which a the weakest feature is removed recursively and the model performance is tested. In the final model 9 features are included: in the final model, the following features were included: tip\_pos, protrusion, length, total\_charge, nr\_charged, identity, similarity, Hydropathy and Hydropathy\_diff \ref{fig:feature_table}.

A final MCC value of 0.99 could be achieved for an ML-model
using the abYmod log file as input as well as the loop 3D-model file
itself. This value slightly dropped to 0.92 if no such log file was
given. This is due to the fact that the template sequence
abYmod used to generate the 3D-model is unknown in the latter case.

The software
was tested on a test-set of antibody structures used in the 2014 and
2011 Antibody Modelling Assessments
\cite{Almagro2011,Almagro2014}. As the results depicted in
Figure~\ref{fig:AMA} show, abYmod achieves results similar to, or better than,
other modelling programs. However, the outliers with very high RMSD
values increase abYmod's RMSD average. The predictor in this work
would aim to identify such outlier 3D-models.

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{flowchart_qualiloop.eps}
  \caption {Simplified pipeline for creating the final machine learning model that will predict 3D-model quality by giving its RMSD range.}
  \label{fig:flow}
\end{figure}

@@

\subsubsection{Scaling}
Normalization and Standardization were tested as scaling methods. In normalization the range of the data is fixed between 0 and 1, while in Standardization the data is re-scaled to fit a Gaussian distribution. Both
approaches are greatly influenced by outliers, and such datapoints are
ideally removed for optimal scaling. Here we define outliers as
datapoints that lie over 1.5 times the interquartile range (IQR) below
the first quartile or above the third quartile. The IQR is defined as
the range between quartile 1, i.e.\ the median of the lower half of the
data, and quartile 3, i.e.\ the median of the upper half of the
data. However, across all features there are a total of 632 outlier
values and removing such a large number of datapoints is not a viable
option. A robust scaler\cite{XXXX} was also used, which uses statistics that are
robust to outliers. The median is set to zero and numerical features
are scaled to the interquartile range.

@@

NLF-encoding \shortcite{Nanni2011} describes a new peptide encoding technique optimized for use with machine learning classifiers. A non-linear Fisher transform is applied to the whole set of physiochemical properties in \shortcite{Kawashima2000}
physiochemical properties are calculated and transformed using a
non-linear Fisher transform for dimensionality reduction.  A vector of
length 19 is produced for each amino acid.

\subsubsection{NLF Encoding}
This method of encoding is detailed by Nanni and Lumini in their paper. It takes many physicochemical properties and transforms them using a Fisher Transform (similar to a PCA) creating a smaller set of features that can describe the amino acid just as well. There are 19 transformed features.

@@

@@

\begin{table}[]
  \centering
  \caption{A summary of how different feature values were calculated.}
  \label{fig:feature_table}

  \begin{adjustbox}{width=\textwidth}

>>>>

\documentclass[12pt]{article}
\bibliographystyle{unsrt}
\usepackage{a4}
\usepackage{graphicx}
\usepackage{url}
\usepackage{color}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{lscape}
\usepackage{longtable}

@@

\begin{abstract}
  Therapeutic antibodies have shown an unprecedented pace of
  development and have brought new hope for the treatment of numerous
  diseases. Bioinformatics tools for modelling antibody structures
  have become invaluable for antibody engineering and the development
  of therapeutic antibodies. The antigen-binding site consists of six
  hypervariable loops, also known as the Complementary Determining
  Regions (CDRs), all of which can generally be modelled with high accuracy,
  except for CDR-H3, which has
  far greater length, sequence and structural variability, 
  making modelling it is considerably harder.

  Many approaches for antibody modelling, such as our
  abYmod software, have been developed. Although such efforts have
  improved prediction accuracy, the results for CDR-H3 are
  still inconsistent and require further improvement. Providing a
  confidence score for the structure predictions would aid in
  differentiating well-modelled structures from incorrectly modelled
  structures, giving the user a clearer understanding of the
  generated 3D-model reliability.

@@

The variable
fragment (Fv) of an antibody contains the six complementarity determining regions
(CDRs, also known as hypervariable loops) which form the antigen binding site.
All except one of these loops can be clustered
into a limited number of `canonical structures'\cite{Al-Lazikani}. Therefore, modelling
these loops with adequate accuracy is commonly
achievable\cite{North2011}.  However, the CDR loop 3 of the 
heavy chain (CDR-H3) has a far greater sequence and length variability due to the
processes of V(D)J recombination and somatic hyper‐mutation and its
structure has remained mostly unclassifiable\cite{Finn2016}. The variety in
structure is so great, that its structural diversity is remarkable
even compared with other protein loops\cite{Regep2017}. It was found
that over 75\% of CDR-H3 loops do not have a sub-{\AA}ngstr\"{o}m non-antibody
structural neighbour, while 30\% of CDR-H3 loops have a
completely unique structure, compared with under 3\% for all non-antibody
loops\cite{Regep2017}.

@@

According to the Kabat definition, the CDR-H3 loop is made up of the
residues H95--H102 (using the Kabat\cite{Kabat1992}, Chothia\cite{Al-Lazikani} or Martin\cite{Abhinandan2008} numbering schemes) in the heavy
chain, with a potential insertion site at position H100. The
possibility of such an insertion of a varying number of residues leads
to a large range of loop lengths, with bovine antibodies being
exceptionally long (Figure~\ref{fig:loopdist}).\lilian{Figure missing!}

For shorter loops, a higher prediction accuracy can be achieved than
for longer CDR-H3 loops. This was also shown in the Antibody Modelling
Assessments (AMA), two blind contests that required researchers to
build three-dimensional structural models (`3D-models' --- used throughout this text to distinguid from machine-learning models `ML-models') from antibody sequences. The CDR-H3 loop
modelling quality achieved at the contests was, on average, much lower
for loops of longer lengths\cite{Almagro2011,Almagro2014}.

Several different approaches for generating 
3D-models from antibody sequences exist including
RosettaAntibody\cite{Sircar2009,Sivasubramanian2009}, 
ABodyBuilder\cite{Leem2016}, PIGSPro\cite{Lepore2017}, Lyra\cite{Klausen2015}, AbLooper\cite{Abanades2022} and our own abYmod (manuscript in preparation).
One of the most
used methods is RosettaAntibody, which implements template selection
and \emph{ab initio} CDR-H3 loop modelling using loop fragments and employing
specific angle restraints which bias the conformational space towards
so-called `kinked' loops\cite{Schoeder2021,Weitzner2017}. In
contrast, ABodyBuilder uses a database search algorithm
(FREAD\cite{Choi2010}) for CDR loop modelling.
abYmod \url{http://abymod.abysis.org/} utilizes extensive canonical
class definitions, \VHVL\ angle prediction and a large database of loop
structures (LoopDB) for CDR-H3 modelling.
Upon inputting an antibody sequence, abYmod assigns the
canonical class using a set of key residues\cite{Martin1996} and where
an exact match is not possible, a nearest class is identified.

abYmod selects light and heavy chain frameworks separately from PDB templates.
First these are selected on the basis of the number of matched
canonical classes and then on the basis of sequence identity.  The
\VHVL\ packing angle is currently selected from the parent that has
the best sequence identity over both chains, but an improved method is
currently in development. Any CDRs where there was no canonical match are then
grafted onto the framework. If there is no template of the correct
length for CDR-H3, the loop is built using LoopDB, a database of
CDR-H3-like loops from all proteins. Finally, Gromacs energy
minimization software is used to optimize the 3D-model. This method has
proven very effective and preliminary analysis suggests the method
achieves comparable results, or outperforms, other modelling software
(see Results).

Using these modelling methods, framework regions can
generally be predicted with great accuracy (better than 1\AA\
\ca~RMSD\cite{Almagro2014}), as one can often find a very similar
structure for the homology modelling process.  However, the CDR loops
are not as easily predicted due to their great diversity. If the
canonical conformation of CDR loops CDR-L1,L2,L3,H1,H2 can be identified, they too
can be modelled rather well, often within 1\AA\ \ca~RMSD. \highlight{for CDR-H3 loops
the The average values are taken from the antibody modelling assessment average} is usually above 3\AA\cite{Almagro2011}. \lilian{Something odd here --- not sure what it's supposed to say!}

ABodyBuilder is a modelling server that provides the user with a
confidence score for each region (e.g.\ CDR-H2) of the antibody
3D-model. The given score is the probability that a specific region
(e.g.\ CDR-H2) will be modelled within a specific RMSD
threshold\cite{Leem2016}. Thus, it can be used to obtain an expected
RMSD value for a given probability (default 75\%). For CDR-H3, this
score is calculated as a function of the loop length.  The confidence
scorer is described as robust, but less accurate in the case of CDR
loops owing to the lack of data\cite{Leem2016}. ABLooper also provides a
confidence metric for the CDR-H3 loop 3D-model, which is estimated by the
diversity of a set of predicted conformations for the same
loop\cite{Abanades2022}. However, it remains unclear whether a high
prediction diversity score points towards loops with multiple
conformations or a low quality 3D-model. Furthermore, it remains unclear
how well the generated diversity score reflects 3D-model
quality\cite{Abanades2022}.

Modelling the CDR-H3 loop is a hurdle for \emph{in silico} development of
therapeutic antibodies. Currently, there is no definite, reliable way
to determine how accurate a generated structural 3D-model is within the
CDR-H3 region. Therefore, we have produced a
user-friendly predictor of CDR-H3 3D-model quality. The predictor will give
the user an RMSD-range in {\AA}ngstr\"{o}ms, in which the generated 3D-model lies
with a high probability.
This information can guide the
user in the antibody engineering process. The user has the choice to
determine whether the 3D-model is to be used as is, or
whether the 3D-model should be re-worked.

@@

The predictive power of any machine learning model (`ML-model') is largely
dependent on the quality and size of the dataset on which it was trained. As
this is a non-linear, complex, multi-class classification problem, a
substantial amount of data was required. Thus, an extensive, verified
dataset of antibody structures called abYbank/AbDb\cite{Ferdous2018},
was utilised (1924 non-redundant
structures). The \ca\ root-mean-square deviation (RMSD) value
between the crystal structures
and modelled structures was calculated (see Methods) and
was used to classify 3D-models.

@@

After creating the feature dataset, it is pre-processed (cleaning,
scaling, encoding, see methods for details). Structures with a
resolution worse than 4\AA\ were removed.
Instances of antibodies in our non-redundant dataset that matched in loop sequence were
not removed as 3D-Models \lilian{Just checking you mean models not structures? Do the structures also differ significantly, or do you really mean that the error varies significantly?} of some of these structures with the same loop
sequence differ significantly.
\lilian{If I understand correctly, you mean that CDR-H3 could have the same sequence in multiple structures, but the overall sequence was different?}
The few large RMSD ranges may stem from
low resolution. For example, the loop sequence with the largest RMSD range 
has multiple structure files linked to it of varying quality, one of which has a resolution of only 3.00\AA. Residue differences near the loop may also
explain the conformational difference of the loop itself, 
even if the loop sequence does not differ. Some of these structures are
complexed while others are not, which may also affect the loop
structure (manuscript in preparation).

The target data (i.e.\ RMSD values) are transformed from numerical
values to nominal values so that they can be used for
classification. In order to define these nominal categories, the total
RMSD range must be divided into categories. This is done either by
creating uniform classes (e.g.\ 1--2\AA, 2--3\AA, etc.), the optimal size of which
must be determined, or by creating balanced classes. When
creating balanced classes, the upper and lower thresholds of a
category are chosen in such a way that each class contains an equal
number of instances. Initially, this approach was chosen to counteract the
skewness of the RMSD distribution. However, this was found to
have a negative effect on the final ML-model's predictive power, so
uniform classes were used.

The RMSD values are also transformed into a set of binary values according to a
list of RMSD thresholds (i.e. a 1 is assigned to above and 0 to below a given threshold). This is done so that binary ML-models can be
trained, which will predict the probability e.g.\ that the 3D-model's RMSD
is above 2\AA, 2.2\AA, 2.4\AA, and so on. \highlight{The number of binary
classifiers incorporated into the first layer} \lilian{You need to describe the overall architecture first so this makes sense. I would have a much simpler version of Figure~\ref{fig:flow} which just shows the ML architecture}  has a great effect on
the final ML-model, the general trend being that the more binary
classifiers are used, the better the nominal prediction.

@@

As some features are in the form of amino acid names, these must be
encoded before they can be passed to a ML-model. The
encoding strategy often determines how efficiently the ML-model learns
and how much information can be extracted. Different strategies were
employed to represent protein sequences numerically, such as BLOSUM62\cite{Henikoff1992} and NLF\cite{Nanni2011} encoding (a non-linear Fisher transform of a large set of physicochemical properties). However, the simple four-feature physiochemical encoding strategy\cite{Abhinandan2010} was implemented for all ML-models, as it was found to be
the most effective, although PCA-3 BLOSUM62, a dimensionality-reduced
BLOSUM62 encoding method, achieved comparable results.
Feature selection was conducted to improve the ML-model's learning
capacity. A high-dimensional feature dataset bears the risk of
introducing excessive noise, facilitating ML-model over-fitting and can be
responsible for an overall decrease in ML-model performance and
stability. Each additional input feature forces the ML-model to
handle a more complex task, which consumes excess computational power
and time and provides more variables leading to over-fitting of the ML-model.

In order to
determine the most effective feature selection method, the
ML-model was trained on different feature sets selected using manual
selection as well as algorithmic selection strategies (see methods).
None of the
feature selection methods was a best fit for all ML-models. To create a ML-model implementing the encoding and feature selection strategies best suited for the specific \highlight{ML-structure} \lilian{What is this?}, a number of different combinations were tested, summarized in Table~\ref{tab:results_table}. Additional ML-Models were discarded due to poor performance.

\begin{table}
  \centering
  \caption{Summary of Machine-Learning Classifier Performances \lilian{Is this just the top-level classifier? You need something providing this sort of info for the final selection for the binary classifiers. What is multi-/single-layer? What is `First-layer weighted'? Is it needed given that i is always Yes for Multi and No for Single? What is `SVC'? Is `Soft Voting' the same as `Voting(soft)'? What are `Basic' features?}}
  \label{tab:results_tableX}

  \small
  \begin{tabular}{lllllll}\hline
    Features        & Feature       & Parameter         & Multi- / & First-    & Classifier    & MCC  \\
                    & Selection     & Optimization      & Single-  & layer     & Type          &      \\
                    & Method        & Method            & layer    & weighted  &               &      \\ \hline
    Basic           & None          & None              & Single   & No        & SVC           & 0.54 \\
    Basic           & None          & GA$^\dag$         & Single   & No        & SVC           & 0.54 \\
    All             & None          & None              & Single   & No        & Random Forest & 0.58 \\
    Selected        & Random Forest & GA                & Single   & No        & Soft Voting   & 0.59 \\
    Selected        & Random Forest & GA                & Multi    & Yes       & XGBoost       & 0.63 \\
    Selected        & Recursive     & GA                & Multi    & Yes       & XGBoost       & 0.79 \\
                    & Feature       &                   &          &           &               &      \\
                    & Elimination   &                   &          &           &               &      \\
    Selected        & Recursive     & GA                & Multi    & Yes       & Decision-Tree & 0.99 \\
                    & Feature       &                   &          &           &               &      \\
                    & Elimination   &                   &          &           &               &      \\
    Selected-NL$^*$ & Recursive     & GA                & Multi    & Yes       & Voting (soft) & 0.92 \\
                    & Feature       &                   &          &           &               &      \\
                    & Elimination   &                   &          &           &               &      \\ \hline
    \multicolumn{7}{l}{$^*$ No log-file features} \\
    \multicolumn{7}{l}{$^\dag$ Genetic algorithm} \\
    \end{tabular}
\end{table}

@@

The best ML-model, and its best hyperparameters, were then determined for
each binary RMSD target. The set of binary ML-models outputs a number of
predictions that give the likelihood of the 3D-model having an RMSD above
the threshold value of the respective ML-model. These predictions are
then added to the feature set, on which a top-layer classifier is then
trained (Figure~\ref{fig:method})\lilian{Incorrect reference}. Thus, a quasi-voting-system is incorporated into the final
classifier, in which a set of weaker classifiers vote on the ML-model
quality.

@@

\subsection{Machine Learning Model Performance}
The overall best final ML-model was composed of several different binary
classifiers, (Figure~\ref{fig:flow}) with an extreme gradient boosting (XGBoost) top-layer
nominal classifier. Features were selected using a recursive feature
elimination algorithm, through which the weakest feature is removed
recursively and the model performance is tested. In the final model, 9
features are included: tip\_pos, protrusion, length, total\_charge, nr\_charged,
identity, similarity, Hydropathy and Hydropathy\_diff
(See Table~\ref{tab:feature_table}).
\lilian{This appears to be the top level. What about a table showing the features used for each of the binary predictors and its MCC and anything else unique to that classifier (e.g. feature selection method)?}

A final MCC value of 0.99 could be achieved for an ML-model
using the abYmod log file as input as well as the loop 3D-model file
itself. This value slightly dropped to 0.92 if no such log file was
given. This is due to the fact that the template sequence
abYmod used to generate the 3D-model is unknown in the latter case
and therefore, sequence identity, similarity and hydropathy difference cannot be calculated. The energy is also not available.
\lilian{There is no option to upload the log file on the web site!}

The software
was tested on a test-set of antibody structures used in the 2014 and
2011 Antibody Modelling Assessments
\cite{Almagro2011,Almagro2014}. As the results depicted in
Figure~\ref{fig:AMA} show, abYmod generally achieves results similar to, or better than,
other modelling programs. However, some outliers with very high RMSD
values increase abYmod's RMSD average. The predictor in this work
would aim to identify such outlier 3D-models.

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{flowchart_qualiloop.eps}
  \caption {Simplified pipeline for creating the final machine learning model that will predict 3D-model quality by giving its RMSD range. \lilian{Make Black and WHite!}}
  \label{fig:flow}
\end{figure}

@@

\subsubsection{Scaling}
Normalization and Standardization were tested as scaling methods. In normalization the range of the data is fixed between 0 and 1, while in Standardization the data is re-scaled to fit a Gaussian distribution. Both
approaches are greatly influenced by outliers and, ideally, such datapoints are
removed for optimal scaling. Here we define outliers as
datapoints that lie over 1.5 times the interquartile range (IQR) below
the first quartile or above the third quartile. The IQR is defined as
the range between quartile 1, i.e.\ the median of the lower half of the
data, and quartile 3, i.e.\ the median of the upper half of the
data. However, across all features there are a total of 632 outlier
values and removing such a large number of datapoints was not a viable
option. A robust scaler\cite{XXXX} \lilian{Citation} was also used, which uses statistics that are
robust to outliers. The median is set to zero and numerical features
are scaled to the interquartile range. \lilian{So which of these scaling methods did you actually use in the end?!}

@@

NLF-encoding \shortcite{Nanni2011} uses multiple physicochemical
properties as described by Kawashima\etal\shortcite{Kawashima2000} and
transforms them using a non-linear Fisher transform (NLF, similar to a
PCA) for dimensionality reduction to produce a vector of length 19.

@@

\lilian{The data are missing --- it would be good to have some
  comparison of the performance of the individual predictors and
  discussion of Table~\ref{tab:results_table}.}

@@

\lilian{There is no text in this section!}

\begin{landscape}
\begin{longtable}{p{3cm}p{10cm}p{10cm}}
  \caption{A summary of how different feature values were calculated.}
  \label{tab:feature_table}\\ \hline
%
  \mbox{Feature} \mbox{Name}  %
  & Description %
  & Method of Calculation\\ \hline
%  
  Sequence %
  & Amino acid sequence of CDR-H3 %
  & Sequence is given in one-letter amino acid codes\\
%  
  Length %
  & Number of residues in CDR-H3 %
  & The number of residues are counted\\
%  
  \mbox{Sequence} \mbox{Identity} %
  & Sequence identity of template loop ($SeqA$) and target loop ($SeqB$). %
  & Calculated by abYmod\\
%  
  \mbox{Sequence} \mbox{Similarity} %
  & Sequence similarity of template loop ($SeqA$) and target loop ($SeqB$). %
  & Calculated by abYmod\\
%  
  \mbox{Loop} \mbox{Protrusion} %
  & Distance of loop residue farthest away from the loop base %
  & See Figure~\protect\ref{fig:loopdist}\\
%  
  \mbox{Protruding} \mbox{residue} %
  & Amino acid code of the most protruding loop residue %
  & See Figure~\protect\ref{fig:loopdist}\\
%  
  Charge %
  & Total charge of the loop %
  & Sum of charges of all residues in loop\\
%  
  \mbox{Charge} \mbox{difference} %
  & Difference in total charge compared with template sequence %
  & Difference between the two summed changes\\
%  
  Hydrophobicity %
  & Mean Hydrophobicity values of loop %
  & Based on Eisenberg consensus values\\
%  
  \mbox{Hydrophobicity} \mbox{difference} %
  & Sum of absolute differences between loop sequence and template loop %
  & Based on Eisenberg consensus values\\
%  
  Accessibility %
  & Total and average accessibility for the loop %
  & Lee and Richards method implemented using `pdbsolv' from BiopTools\\
%  
  \mbox{Sidechain} \mbox{Accessibility} %
  & Total and average side-chain accessibility for the loop %
  & Lee and Richards method implemented using `pdbsolv' from BiopTools\\
%  
  \mbox{Relative} \mbox{Accessibility}  %
  & Total and average relative accessibility for the loop %
  & Lee and Richards method implemented using `pdbsolv' from BiopTools\\
%  
  \mbox{Relative} \mbox{Sidechain} \mbox{Accessibility} %
  & Total and average relative side-chain accessibility for the loop %
  & Lee and Richards method implemented using `pdbsolv' from BiopTools\\
%  
  `Happiness' %
  & Happiness score, taking accessibility and hydropobicity into account. If a residue is `happy' it will not be a buried hydrophilic or a surface hydrophobic residue %
  & Hydrophobicity values are normalized to a range of -1 to +1. Mean accessibility values are calculated as above. If hydrophobicity of loop is $<0$:
  $Happiness = 1+Hydrophobicity(1-Accessibility)$
  Otherwise:
  $Happiness = 1-(Hydrophobicity Accessibility)$\\
%  
  \mbox{Number} \mbox{of} \mbox{Contacts} %
  & Number of $\le 3.5$\AA\ mainchain or sidechain contacts made by residues of the loop %
    Contacts made with residues within and outside the loop are counted separately and as a total. The ratio of inside \emph{vs.} outside is also calculated. %
  & Modified version of `rangecontacts' from BiopTools. \\
%  
  Energy %
  & Potential energy of the model. %
  & Calculated by Gromacs during the energy minimization step in abYmod. \\
%
  \mbox{Lowest} \mbox{BLOSUM62} \mbox{Scoring} \mbox{Residue} \mbox{Pair} %
  & Each possible residue pair in CDR-H3 is scored by their BLOSUM 62 score. %
    The lowest scoring pair's BLOSUM62 value is combined with their residue separation to form the metric. %
  & Separation is the nuber of residues between the worst residue pair (i.e.\ the lowest BLOSUM62 score achieved by a residue pair), %
    the metric is calculated as: $WorstBLOSUM = -log_2(separation)(worst score)$\\ \hline
  \end{longtable}
  \lilian{You need more description of the BLOSUM separation metric in the methods}
\end{landscape}
